My title

### 2024-03-14 paper/paper.qmd

# Model

For our study, we employ a technique called multilevel regression with post-stratification (MRP). This approach involves creating a model based on a smaller data set, such as our survey data, and then extending the model's findings to a larger population.

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

>>>>

# Model
For our study, we employ a technique called multilevel regression with post-stratification (MRP). This approach involves creating a model based on a smaller data set, such as our survey data, and then extending the model's findings to a larger population.

```{r}
#| echo: false
#| message: false
#| warning: false
model <- survey_model

# Assuming 'model' is your model object from rstanarm
library(broom.mixed)

coefficients <- broom.mixed::tidy(model, conf.int = TRUE)

# Assuming you have knitr and kableExtra already installed and loaded
library(knitr)
library(kableExtra)

knitr::kable(coefficients,
             caption = "Coefficients from the Model",
             digits = 2) %>%
  kableExtra::kable_styling(latex_options = "scale_down")

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-coefficient-estimates
#| fig-cap: Coefficient Estimates

model <- survey_model

coefficients <- broom.mixed::tidy(model, conf.int = TRUE)
# plot our coefficients with error bars to show the upper and lower
# estimates for the coefficients
coefficients %>% ggplot(aes(estimate, term)) +
  geom_point() +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) +
  labs(title = "Coefficient Estimates",
       x = "Estimate", y = "Coefficient") +
  theme(axis.text.y = element_text(size = 5))
```
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
